Pillar 2 - Topic Modeling

### 2019-02-15 Pillar 2 - Topic Modeling.Rmd
save cached results in folder `Cache`
find ideal # topics for topic model

```{r LDA number topics, eval = FALSE}

my_control <- list(

  burnin = 500
  iter   = 2000,
  thin   = 100

result <- FindTopicsNumber(

  d_description_cast,
  topics = seq(from = 20, to = 150, by = 5),
  metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
  method = "Gibbs",
  control = my_control,
  mc.cores = 1L

save(result,
     file = "LDA_ntopics.RDATA")
```

```{r LDA number topics plot}
load("LDA_ntopics.RDATA")
FindTopicsNumber_plot(result)
```

## Fitting Model
```{r my_cast_tdm}
my_cast_tdm <- function(data, level) data %>%
  count(`Course ID`, word) %>%
  cast_dtm(`Course ID`, word, n)

@@

@@

## Visualization
### Functions
```{r LDA prepare}
prepare_data_LDA_beta <- function(results){

@@

```{r LDA visualize}
visualize_LDA_beta <- function(data_prepared, id_plot = "test"){

@@

```{r LDA visualize all distrib}
visualize_LDA_all_distrib <- function(data, level = Course, id_plot = "test"){

@@

```{r LDA visualize all level}
visualize_LDA_all_level <- function(data, id_plot = "test"){

@@

### Plots
```{r LDA plot, cache = TRUE}
load("LDA.RDATA")

@@

```{r label, eval = FALSE}
tidy(LDA_manual_10, "beta") %>%
  filter(beta > 1e-3) %>%
  bind_tf_idf(term = term, document = topic, n = beta) %>%
  group_by(topic) %>%
  top_n(10, tf_idf) %>%
  arrange(topic, desc(tf_idf))

>>>>

```{r my_cast_tdm}
my_cast_tdm <- function(data, level) data %>%
  count(`Course ID`, word) %>%
  cast_dtm(`Course ID`, word, n)

@@

```{r}
my_control <- list(

  burnin = 500,
  iter   = 2000,
  thin   = 100

)
```

```{r}
my_FindTopicsNumber <- function(data_cast, n_topics){

  FindTopicsNumber(

  dtm = data_cast,
  topics = n_topics,
  metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
  method = "Gibbs",
  control = my_control,
  mc.cores = 1L

```{r}
start.time <- Sys.time()

result_description <- d_description_cast %>% my_FindTopicsNumber(n_topics = seq(from = 5, to = 100, by = 1))

end.time <- Sys.time()
time.taken <- end.time - start.time

save(result_descrition,
     file = "Output/LDA_ntopics_description.RDATA")

print(time.taken)
```

```{r}
start.time <- Sys.time()

result_overview <- d_overview_cast %>% my_FindTopicsNumber(n_topics = seq(from = 5, to = 100, by = 1))

end.time <- Sys.time()
time.taken <- end.time - start.time

save(result_overview ,
     file = "Output/LDA_ntopics_overview.RDATA")

print(time.taken)
```

```{r, eval = F}
start.time <- Sys.time()

result_manual <- d_manual_cast %>% my_FindTopicsNumber(n_topics = seq(from = 5, to = 155, by = 10))

end.time <- Sys.time()
time.taken <- end.time - start.time

save(result_manual,
     file = "Output/LDA_ntopics_manual.RDATA")

print(time.taken)
```

from 20, to 40, by 5 topics takes
22min for overview
11min for description
5.5hrs for manuals

```{r LDA number topics plot}

load("Output/LDA_ntopics_description.RDATA")

load("Output/LDA_ntopics_overview.RDATA")

load("Output/LDA_ntopics_manual.RDATA")

result_descrition %>%
  select(-Griffiths2004) %>%
  FindTopicsNumber_plot

result_overview %>%
  select(-Griffiths2004) %>%
  FindTopicsNumber_plot

result_manual %>%
  select(-Griffiths2004) %>%
  FindTopicsNumber_plot

```

## Fitting Model

@@

## Visualization
### Functions
```{r LDA prepare, eval = F}
prepare_data_LDA_beta <- function(results){

@@

```{r LDA visualize, eval = F}
visualize_LDA_beta <- function(data_prepared, id_plot = "test"){

@@

```{r LDA visualize all distrib, eval = F}
visualize_LDA_all_distrib <- function(data, level = Course, id_plot = "test"){

@@

```{r LDA visualize all level, eval = F}
visualize_LDA_all_level <- function(data, id_plot = "test"){

@@

### Plots
```{r LDA plot, cache = TRUE, eval = F}
load("LDA.RDATA")

@@

```{r label, eval = FALSE, eval = F}
tidy(LDA_manual_10, "beta") %>%
  filter(beta > 1e-3) %>%
  bind_tf_idf(term = term, document = topic, n = beta) %>%
  group_by(topic) %>%
  top_n(10, tf_idf) %>%
  arrange(topic, desc(tf_idf))
